Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm

### 2023-11-09 paper/SST/3-main.tex
Update graphics path and remove isolated_mac.png.
modify results in case study

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
% \graphicspath{ {./figures/} }
% \graphicspath{ {../figures/} }
\graphicspath{ {../../attachments} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers

@@

After obtaining the SPs, the MACs of the three RBS structures with four batteries are calculated using the proposed greedy algorithm, and the results are shown in Tabs. \ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}, each of which contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ when the system output reaches the MAC.
The correspond switch-control schemes are shown as blue-highlighted electric current in Figs. \ref{fig:e4-mac}, \ref{fig:f4-mac}, and \ref{fig:e2f2-mac}, respectively.
To verify and compare the proposed greedy algorithm, we also used the brute-force algorithm, which iterates through all possible switch states, and the heuristic algorithms (SA and GA) to calculate the MAC of the same RBSs. 
The final results of the brute-force algorithm are the same as the ones of the greedy algorithm, which are shown in Tabs. \ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}.
But, the brute-force algorithm counts all possible switch states, which equates to $2^{15}$, $2^{13}$, and $2^{19}$ structures, respectively.
The two heuristic algorithms' temporal evaluation of the objective values during the iteration process are shown in Figs. \ref{fig:e4-alg}, \ref{fig:f4-alg}, and \ref{fig:e2f2-alg}, respectively, compared with the proposed greedy algorithm.

@@

We next consider the RBS structure in Fig. \ref{fig:study-stru-my} with two, four, and six batteries.
The result of four-battery structure has been shown in Tab. \ref{tab:study-results-my}, Figs. \ref{fig:e2f2-mac}, and \ref{fig:e2f2-alg}. 
The structures and final switch-control schemes of the remaining two-battery and six-battery systems are illustrated in Figs. \ref{fig:e2f1-mac} and \ref{fig:e2f3-mac}, respectively. 
And the temporal evolution of the objective values throughout the iteration process are shown in Figs. \ref{fig:e2f1-alg} and \ref{fig:e2f3-alg}, respectively.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
% \graphicspath{ {./figures/} }
\graphicspath{ {../figures/} }
% \graphicspath{ {../../attachments} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers

@@

After obtaining the SPs, the MACs of the three RBS structures with four batteries are calculated using the proposed greedy algorithm, and the results are shown in Tabs. \ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}, each of which contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ when the system output reaches the MAC.
The correspond switch-control schemes are shown as blue-highlighted electric current in Figs. \ref{fig:e4-mac}, \ref{fig:f4-mac}, and \ref{fig:e2f2-mac}, respectively.
To verify and compare the proposed greedy algorithm, we also used the brute-force algorithm, which iterates through all possible switch states, and the heuristic algorithms (SA and GA) to calculate the MAC of the same RBSs. 
The final results of the brute-force algorithm are the same as the ones of the greedy algorithm, which are shown in Tabs. \ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}.
But, the brute-force algorithm counts all possible switch states, which equates to $2^{15}$, $2^{13}$, and $2^{19}$ structures, respectively.
The two heuristic algorithms' temporal evaluation of the objective values during the iteration process are shown in Figs. \ref{fig:e4-alg}, \ref{fig:f4-alg}, and \ref{fig:e2f2-alg}, respectively, compared with the proposed greedy algorithm. 
Comparing to the SA and GA, the proposed greedy algorithm solves the correct results with fewer iteration steps.

@@

We next examine the RBS configuration depicted in Fig. \ref{fig:study-stru-my}, which consists of two, four, and six batteries.
The results for the four-battery configuration are presented in Tab. \ref{tab:study-results-my}, Figs. \ref{fig:e2f2-mac}, and \ref{fig:e2f2-alg}.
The structures and final switch-control schemes for the two-battery and six-battery systems are illustrated in Figs. \ref{fig:e2f1-mac} and \ref{fig:e2f3-mac}, respectively.
Furthermore, the temporal evolutions of the objective values throughout the iteration process are shown in Figs. \ref{fig:e2f1-alg} and \ref{fig:e2f3-alg}, respectively.
The proposed greedy algorithm is still the one that converges the fastest and achieves the correct MAC. 
And the SA algorithm fails to obstain the correct MAC within the given iteration steps in the case of six-battery RBS structure.
